---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stopwatch

<!-- badges: start -->
<!-- badges: end -->

The goal of stopwatch is to make executing long running code a better experience. Long running code can seriously hurt productivity, because your concentration is often brokne when you are waiting for an expression to finish evaluating. stopwatch will give you an idea of how long 

## Installation

stopwatch is not on CRAN. You can install stopwatch from GitHub with:

```{r, eval=FALSE}
remotes::install_github('JamesM131/stopwatch')
```

## Example

Loading the stopwatch package will automatically override the default variable assignment. The new assignment operator will start a timer in the console that will count upwards while code is executing, and will run `beepr::beep()` when the execution has finished if it took longer than 3 seconds. 

```{r example}
library(stopwatch)
```


A stopwatch timer can also be created directly, which is useful if the long running code is not being assigned to a variable. This is done like so:

```{r direct-timer}
start_timer()
stop_timer()
```


## Notes

* The timer is slightly slower than my phone's built in stopwatch on a crude measurement. I'm looking at adding a test for that and possibly a timing correction. 
* Ideally this package would override automatic printing along with assignment, but the implementation of that seems trickier. 
* If stopwatch's modified assignment causes problems in your code, it can be removed by running `rm('<-')`

